SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-05 My-Papers/SpecHunter/overview.tex
writing more overview

We pick the next node based on an algorithm called D-separation

@@

Global propagations rely on a process which we call ``knowledge transfer''. It
relies on the

>>>>

We pick the next node based on an decision procedure called \emph{D-separation}.
This algorithm, given the following:

\begin{itemize}
\item A Bayesian Network (hence, a DAG),
\item A set of nodes $x$,
\item Another set of nodes $y$,
\item Yet another set of nodes $z$,
\end{itemize}

tells if nodes of $x$ may be probabilistically independent of those in $y$. We
utilize this algorithm like the following: For all nodes in a Bayesian network in
hand, we set $x$ as a singleton set of node $n_1$, $y$ as a singleton set of
node $n_2$, and $z$ as the set of all nodes that we have asked of its value so
far. This way, we can count the number of nodes that are sure to be
probabilisitically dependent to that node.

% 이 알고리즘은 그냥 말로 설명하려고 했는데 figure로 따로 빼야겠다.

% nx.d_separated(graph_for_reference, {node}, {other_node}, set(current_asked))

We use \emph{networkx}'s implementation of D-separation.

@@

Global propagations rely on a process which we call ``knowledge transfer''. It
relies on three major relations:

\begin{itemize}
\item
\item
\item
\end{itemize}
